Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics

### 2020-01-13 paper/paper.Rmd
two references sections fixed

<!-- Other cartograms -->
Alternative algorithms make various trade offs between familiar shapes and representation of geographic units. The non-contiguous cartogram method [@NAC] keeps the shapes of geographic units intact, and changes the size of the shape. This method disconnects areas creating empty space on the display losing the continuity of the spatial display of the statistic. The Dorling cartogram [@ACTUC] represents each unit as a circle, sized according to the value of the statistic. The neighbour relationships are mostly maintained by how the circles touch. A similar approach was pioneered by Raisz [-@RSCW], using rectangles that tile to align borders of neighbours [@CDWCS]. A thorough review of the array of methods, as suitable for cancer atlas displays is available in XXX.

@@

Australia is used for the study, with Statistical Area 2 (SA2) (XXX REF) as the geographic units. The results should apply broadly to any other geographic area of interest.

@@

Data is generated for each of the trend models, with four replicates, and each displayed both as a choropleth and as a hexagon tile map, which yields 12 data sets, and 24 data plots. This set of displays is divided in half, providing two sets of 12 displays, Group A and Group B. Participants were randomly allocated to Group A or B. Participants saw a data set only once, with as a choropleth or as a hexagon tile map. Table \ref{fig:exp-design} summarises the design. (XXX Maybe replace this table with your diagram illustrating the design??)

@@

For spatial data, null data is stationary data, where the mean, variance and spatial dependence are constant over the geographic units. Stationary data is specified by a variogram model (XXX REF). Simulating from a variogram model, where the spatial dependence is specified, generates the stationary spatial data used for the null plots.  The parameters for the Gaussian model were sill=1, range=0.3 with the variance generated by a standard normal distribution.

@@

## Web app collecting responses

XXX Describe the details of the taipan app used to collect responses

Data was collected through a web application containing the online survey.
Each participant used the internet to access the survey.
The data collection took place using a secure link between the survey web application and the googlesheet used to store results. The application would first connect to the googlesheet using the googlesheets [@sheets] R package, and interacted again at the completion of the survey by adding the participant's responses to the 12 displays as 12 rows of data in the googlesheet.

@@

Participants were recruited for to evaluate lineups from the Figure Eight crowd sourcing platform [@figeight].
The lineup protocol expects that the participants are uninvolved judges with no prior knowledge of the data, to avoid inadvertently affecting results. Potential participants needed to have achieved level 2 or level 3 from prior work. The participants were chosen as they have experience with survey tasks that involve evaluating images XXX Did we really choose participants this way??). All participants were at least 18 years old.

@@

Acknowledgements
==============

The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualizations. They would also like to thank Kerrie Mengersen and Dr. Earl Duncan for suggestions and comments.

All code to generate the data, of the web app that collected participants responses, conduct the analysis, and produce this manuscript are available on XXX.

- Additional analysis of the experimental results
- Training materials used for the participants
- 24 lineups used in the experiment
- 12 data sets used to construct the lineups

References {#references .numbered}
==========

<!-- An example of a floating figure using the graphicx package. -->
<!-- Note that \label must occur AFTER (or within) \caption. -->
<!-- For figures, \caption should occur after the \includegraphics. -->
<!-- Note that IEEEtran v1.7 and later has special internal code that -->
<!-- is designed to preserve the operation of \label within \caption -->
<!-- even when the captionsoff option is in effect. However, because -->
<!-- of issues like this, it may be the safest practice to put all your -->
<!-- \label just after \caption rather than within \caption{}. -->

<!-- Reminder: the "draftcls" or "draftclsnofoot", not "draft", class -->
<!-- option should be used if it is desired that the figures are to be -->
<!-- displayed while in draft mode. -->

<!-- \begin{figure}[!t] -->
<!-- \centering -->
<!-- \includegraphics[width=2.5in]{myfigure} -->
<!-- where an .eps filename suffix were assumed under latex,  -->
<!-- and a .pdf suffix were assumed for pdflatex; or what has been declared -->
<!-- via \DeclareGraphicsExtensions. -->
<!-- \caption{Simulation results for the network.} -->
<!-- \label{fig_sim} -->
<!-- \end{figure} -->

<!-- Note that the IEEE typically puts floats only at the top, even when this -->
<!-- results in a large percentage of a column being occupied by floats. -->

<!-- An example of a double column floating figure using two subfigures. -->
<!-- (The subfig.sty package must be loaded for this to work.) -->
<!-- The subfigure \label commands are set within each subfloat command, -->
<!-- and the \label for the overall figure must come after \caption. -->
<!-- \hfil is used as a separator to get equal spacing. -->
<!-- Watch out that the combined width of all the subfigures on a  -->
<!-- line do not exceed the text width or a line break will occur. -->

<!-- \begin{figure*}[!t] -->
<!-- \centering -->
<!-- \subfloat[Case I]{\includegraphics[width=2.5in]{box}% -->
<!-- \label{fig_first_case}} -->
<!-- \hfil -->
<!-- \subfloat[Case II]{\includegraphics[width=2.5in]{box}% -->
<!-- \label{fig_second_case}} -->
<!-- \caption{Simulation results for the network.} -->
<!-- \label{fig_sim} -->
<!-- \end{figure*} -->

<!-- Note that often IEEE papers with subfigures do not employ subfigure -->
<!-- captions (using the optional argument to \subfloat[]), but instead will -->
<!-- reference/describe all of them (a), (b), etc., within the main caption. -->
<!-- Be aware that for subfig.sty to generate the (a), (b), etc., subfigure -->
<!-- labels, the optional argument to \subfloat must be present. If a -->
<!-- subcaption is not desired, just leave its contents blank, -->
<!-- e.g., \subfloat[]. -->

\newpage

@@

@@

<!-- An example of a floating figure using the graphicx package. -->
<!-- Note that \label must occur AFTER (or within) \caption. -->
<!-- For figures, \caption should occur after the \includegraphics. -->
<!-- Note that IEEEtran v1.7 and later has special internal code that -->
<!-- is designed to preserve the operation of \label within \caption -->
<!-- even when the captionsoff option is in effect. However, because -->
<!-- of issues like this, it may be the safest practice to put all your -->
<!-- \label just after \caption rather than within \caption{}. -->

<!-- Reminder: the "draftcls" or "draftclsnofoot", not "draft", class -->
<!-- option should be used if it is desired that the figures are to be -->
<!-- displayed while in draft mode. -->

<!-- \begin{figure}[!t] -->
<!-- \centering -->
<!-- \includegraphics[width=2.5in]{myfigure} -->
<!-- where an .eps filename suffix were assumed under latex,  -->
<!-- and a .pdf suffix were assumed for pdflatex; or what has been declared -->
<!-- via \DeclareGraphicsExtensions. -->
<!-- \caption{Simulation results for the network.} -->
<!-- \label{fig_sim} -->
<!-- \end{figure} -->

<!-- Note that the IEEE typically puts floats only at the top, even when this -->
<!-- results in a large percentage of a column being occupied by floats. -->

<!-- An example of a double column floating figure using two subfigures. -->
<!-- (The subfig.sty package must be loaded for this to work.) -->
<!-- The subfigure \label commands are set within each subfloat command, -->
<!-- and the \label for the overall figure must come after \caption. -->
<!-- \hfil is used as a separator to get equal spacing. -->
<!-- Watch out that the combined width of all the subfigures on a  -->
<!-- line do not exceed the text width or a line break will occur. -->

<!-- \begin{figure*}[!t] -->
<!-- \centering -->
<!-- \subfloat[Case I]{\includegraphics[width=2.5in]{box}% -->
<!-- \label{fig_first_case}} -->
<!-- \hfil -->
<!-- \subfloat[Case II]{\includegraphics[width=2.5in]{box}% -->
<!-- \label{fig_second_case}} -->
<!-- \caption{Simulation results for the network.} -->
<!-- \label{fig_sim} -->
<!-- \end{figure*} -->

<!-- Note that often IEEE papers with subfigures do not employ subfigure -->
<!-- captions (using the optional argument to \subfloat[]), but instead will -->
<!-- reference/describe all of them (a), (b), etc., within the main caption. -->
<!-- Be aware that for subfig.sty to generate the (a), (b), etc., subfigure -->
<!-- labels, the optional argument to \subfloat must be present. If a -->
<!-- subcaption is not desired, just leave its contents blank, -->
<!-- e.g., \subfloat[]. -->

>>>>

<!-- Other cartograms -->
Alternative algorithms make various trade offs between familiar shapes and representation of geographic units. The non-contiguous cartogram method [@NAC] keeps the shapes of geographic units intact, and changes the size of the shape. This method disconnects areas creating empty space on the display losing the continuity of the spatial display of the statistic. The Dorling cartogram [@ACTUC] represents each unit as a circle, sized according to the value of the statistic. The neighbour relationships are mostly maintained by how the circles touch. A similar approach was pioneered by Raisz [-@RSCW], using rectangles that tile to align borders of neighbours [@CDWCS]. There have been thorough reviews of the array of methods, as suitable for cancer atlas displays [@review], [@BCM].

@@

Australia is used for the study, with Statistical Area 2 (SA2) [@abs2016] as the geographic units. The results should apply broadly to any other geographic area of interest.

@@

Data is generated for each of the trend models, with four replicates, and each displayed both as a choropleth and as a hexagon tile map, which yields 12 data sets, and 24 data plots. This set of displays is divided in half, providing two sets of 12 displays, Group A and Group B. Participants were randomly allocated to Group A or B. Participants saw a data set only once, with as a choropleth or as a hexagon tile map. Table \ref{fig:exp-design} summarises the design.

@@

For spatial data, null data is stationary data, where the mean, variance and spatial dependence are constant over the geographic units. Stationary data is specified by a variogram model [@POG]. Simulating from a variogram model, where the spatial dependence is specified, generates the stationary spatial data used for the null plots.  The parameters for the Gaussian model were sill=1, range=0.3 with the variance generated by a standard normal distribution.

@@

## Web application to collect responses

The taipan [@taipan] package for R was used to create the survey web application. 
This structure was altered to collect responses regarding participants demographics and their survey responses.
The survey app contained three tabs, participants were first shown the demographics and consent page.
This asked participants for their Figure-Eight contributor ID, and their consent to the responses being used for analysis. The demographics collected included participants' preferred pronoun, the highest level of education achieved, their age range and whether they had lived in Australia.

After submitting these responses, the survey application switched to the tab of lineups and associated questions. This allowed participants to easily move through the twelve displays and provide their choice, reason for their choice, and level of certainty.

When participants completed the twelve evaluations the survey application triggered a data analysis script. This created a data set with one row per evaluation. Along with the responses to the three questions, the script added the title of the image, which indicated the type of map display, the type of distribution hidden in the lineup, and the location of the data plot. It also calculated the time taken by participant to view each lineup.

Each participant used the internet to access the survey.
The data transfer from the web application to the data set took place using a secure link to the googlesheet used to store results. The application connected to the googlesheet using the googlesheets [@sheets] R package when participants opened the application, and interacted again when participants chosen to submit the survey and indicate their completion. At this time it added the participant's responses to the twelve lineup displays as twelve rows of data in the googlesheet.

@@

Participants were recruited to evaluate lineups from the Figure Eight crowdsourcing platform [@figeight].
The lineup protocol expects that the participants are uninvolved judges with no prior knowledge of the data, to avoid inadvertently affecting results. Potential participants needed to have achieved level 2 or level 3 from prior work. The participants were chosen as they have experience with survey tasks that involve evaluating images XXX Did we really choose participants this way??). All participants were at least 18 years old.

@@

@@

- Additional analysis of the experimental results
- Survey procedure including training materials for the participants
- 24 lineups as images, that were used in the experiment
- 12 data sets used to construct the lineups

@@

### 2020-01-13 paper/paper.tex
two references sections fixed

Alternative algorithms make various trade offs between familiar shapes and representation of geographic units. The non-contiguous cartogram method {[}\protect\hyperlink{ref-NAC}{8}{]} keeps the shapes of geographic units intact, and changes the size of the shape. This method disconnects areas creating empty space on the display losing the continuity of the spatial display of the statistic. The Dorling cartogram {[}\protect\hyperlink{ref-ACTUC}{7}{]} represents each unit as a circle, sized according to the value of the statistic. The neighbour relationships are mostly maintained by how the circles touch. A similar approach was pioneered by Raisz {[}\protect\hyperlink{ref-RSCW}{9}{]}, using rectangles that tile to align borders of neighbours {[}\protect\hyperlink{ref-CDWCS}{10}{]}. A thorough review of the array of methods, as suitable for cancer atlas displays is available in XXX.

@@

In order to assess the effectiveness of the hexagon tile map, the lineup protocol {[}\protect\hyperlink{ref-GIIV}{3}{]} from visual inference procedures is employed. The procedures for doing a power comparison of competing plot designed, outlined in {[}\protect\hyperlink{ref-GTPCCD}{12}{]}, are followed. The approach mirrors classical statistical inference.

In classical statistical inference hypothesis testing is conducted by comparing the value of a test statistic on a standard reference distribution, computed assuming the null hypothesis is true. If the value is extreme, the null hypothesis is rejected, because the test statistic value is unlikely to have been so extreme if it was true. In the lineup protocol, the plot plays the role of the test statistic, and the data plot is embedded in a field of null plots. Defining the plot using a grammar of graphics {[}\protect\hyperlink{ref-ggplot2}{13}{]} makes it a functional mapping of the variables and thus, it can be considered to be a statistic. With the same data, two different plots can be considered to be competing statistics, one possibly a more powerful statistic than the other.

@@

Australia is used for the study, with Statistical Area 2 (SA2) (XXX REF) as the geographic units. The results should apply broadly to any other geographic area of interest.

@@

For spatial data, null data is stationary data, where the mean, variance and spatial dependence are constant over the geographic units. Stationary data is specified by a variogram model (XXX REF). Simulating from a variogram model, where the spatial dependence is specified, generates the stationary spatial data used for the null plots. The parameters for the Gaussian model were sill=1, range=0.3 with the variance generated by a standard normal distribution.

The R package \texttt{gstat} {[}\protect\hyperlink{ref-gstat}{14}{]} was used to simulate 144 null sets, 12 data sets for each plot in a lineup, and 12 sets for 12 lineups.

@@

\hypertarget{web-app-collecting-responses}{%
\subsection{Web app collecting responses}\label{web-app-collecting-responses}}

XXX Describe the details of the taipan app used to collect responses

Data was collected through a web application containing the online survey.
Each participant used the internet to access the survey.
The data collection took place using a secure link between the survey web application and the googlesheet used to store results. The application would first connect to the googlesheet using the googlesheets {[}\protect\hyperlink{ref-sheets}{15}{]} R package, and interacted again at the completion of the survey by adding the participant's responses to the 12 displays as 12 rows of data in the googlesheet.

@@

Participants were recruited for to evaluate lineups from the Figure Eight crowd sourcing platform {[}\protect\hyperlink{ref-figeight}{16}{]}.
The lineup protocol expects that the participants are uninvolved judges with no prior knowledge of the data, to avoid inadvertently affecting results. Potential participants needed to have achieved level 2 or level 3 from prior work. The participants were chosen as they have experience with survey tasks that involve evaluating images XXX Did we really choose participants this way??). All participants were at least 18 years old.

@@

The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model.
The R {[}\protect\hyperlink{ref-RCore}{17}{]} \texttt{glmer()} function in the {[}\protect\hyperlink{ref-lme4}{18}{]} package implements generalised linear mixed effect models. The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:

@@

Computation will be done using R {[}\protect\hyperlink{ref-RCore}{17}{]}, with the \texttt{lme4} package {[}\protect\hyperlink{ref-lme4}{18}{]}.

@@

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualizations. They would also like to thank Kerrie Mengersen and Dr.~Earl Duncan for suggestions and comments.

All code to generate the data, of the web app that collected participants responses, conduct the analysis, and produce this manuscript are available on XXX.

\begin{itemize}
\tightlist
\item
  Additional analysis of the experimental results
\item
  Training materials used for the participants
\item
  24 lineups used in the experiment
\item
  12 data sets used to construct the lineups
\end{itemize}

@@

The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualizations, and Professor Kerrie Mengersen and Dr Earl Duncan for regular meetings filled with suggestions and comments. Mitchell O'Hara-Wild was a co-developer of the taipan {[}\protect\hyperlink{ref-taipan}{19}{]} R package for image tagging, used as the base for the web app constructed to collect participant evaluations of lineups. We are thankful for the NUMBATs (Non-Uniform Monash Business Analytics Team) for participating in the pilot study that helped to assess the experimental design and determine an appropriate sample size for the study.

@@

The analysis of the work was completed in R {[}\protect\hyperlink{ref-RCore}{17}{]} with the use of the following packages:

\begin{itemize}
\tightlist
\item
  For document creation: rmarkdown {[}\protect\hyperlink{ref-rmarkdown}{20}{]}, rticles {[}\protect\hyperlink{ref-rticles}{21}{]}, knitr {[}\protect\hyperlink{ref-knitr}{22}{]}.
\item
  For lineup creation and data analysis: tidyverse {[}\protect\hyperlink{ref-tidyverse}{23}{]}, nullabor {[}\protect\hyperlink{ref-nullabor}{24}{]}, ggthemes {[}\protect\hyperlink{ref-ggthemes}{25}{]}, RColorBrewer {[}\protect\hyperlink{ref-RColorBrewer}{26}{]}.
\item
  For image displays: cowplot {[}\protect\hyperlink{ref-cowplot}{27}{]}, png {[}\protect\hyperlink{ref-png}{28}{]}, grid {[}\protect\hyperlink{ref-grid}{29}{]}.
\item
  For modelling and presentation of models: gstat {[}\protect\hyperlink{ref-gstat}{14}{]}, lme4 {[}\protect\hyperlink{ref-lme4}{18}{]}, kableExtra {[}\protect\hyperlink{ref-kableExtra}{30}{]}.
\end{itemize}

@@

\hypertarget{references-1}{%
\section{References}\label{references-1}}

@@

\leavevmode\hypertarget{ref-BCHLLSW09}{}%
11. Buja A, Cook D, Hofmann H, Lawrence M, Lee E-K, Swayne DF, Wickham H (2009) Statistical inference for exploratory data analysis and model diagnostics. Philosophical Transactions of the Royal Society, A (Invited) 367:4361--4383

\leavevmode\hypertarget{ref-GTPCCD}{}%
12. Hofmann H, Follett L, Majumder M, Cook D (2012) Graphical tests for power comparison of competing designs. IEEE Transactions on Visualization and Computer Graphics 18:2441--2448

\leavevmode\hypertarget{ref-ggplot2}{}%
13. Wickham H (2009) Ggplot2: Elegant graphics for data analysis. Springer New York

\leavevmode\hypertarget{ref-gstat}{}%
14. Gräler B, Pebesma E, Heuvelink G (2016) Spatio-temporal interpolation using gstat. The R Journal 8:204--218

\leavevmode\hypertarget{ref-sheets}{}%
15. Bryan J, Zhao J (2018) Googlesheets: Manage google spreadsheets from r.

\leavevmode\hypertarget{ref-figeight}{}%
16. (2019) The essential high-quality data annotation platform. Figure Eight

\leavevmode\hypertarget{ref-RCore}{}%
17. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria

\leavevmode\hypertarget{ref-lme4}{}%
18. Bates D, Mächler M, Bolker B, Walker S (2015) Fitting linear mixed-effects models using lme4. Journal of Statistical Software 67:1--48

\leavevmode\hypertarget{ref-taipan}{}%
19. Kobakian S, O'Hara-Wild M (2018) Taipan: Tool for annotating images in preparation for analysis.

\leavevmode\hypertarget{ref-rmarkdown}{}%
20. Xie Y, Allaire JJ, Grolemund G (2018) R markdown: The definitive guide. Chapman; Hall/CRC, Boca Raton, Florida

\leavevmode\hypertarget{ref-rticles}{}%
21. Allaire J, Xie Y, R Foundation, et al (2019) Rticles: Article formats for r markdown.

\leavevmode\hypertarget{ref-knitr}{}%
22. Xie Y (2014) Knitr: A comprehensive tool for reproducible research in R. Implementing reproducible computational research

\leavevmode\hypertarget{ref-tidyverse}{}%
23. Wickham H, Averick M, Bryan J, et al (2019) Welcome to the tidyverse. Journal of Open Source Software 4:1686

\leavevmode\hypertarget{ref-nullabor}{}%
24. Wickham H, Chowdhury NR, Cook D, Hofmann H (2018) Nullabor: Tools for graphical inference.

\leavevmode\hypertarget{ref-ggthemes}{}%
25. Arnold JB (2019) Ggthemes: Extra themes, scales and geoms for 'ggplot2'.

\leavevmode\hypertarget{ref-RColorBrewer}{}%
26. Neuwirth E (2014) RColorBrewer: ColorBrewer palettes.

\leavevmode\hypertarget{ref-cowplot}{}%
27. Wilke CO (2019) Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'.

\leavevmode\hypertarget{ref-png}{}%
28. Urbanek S (2013) Png: Read and write png images.

\leavevmode\hypertarget{ref-grid}{}%
29. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria

\leavevmode\hypertarget{ref-kableExtra}{}%
30. Zhu H (2019) KableExtra: Construct complex table with 'kable' and pipe syntax.

>>>>

Alternative algorithms make various trade offs between familiar shapes and representation of geographic units. The non-contiguous cartogram method {[}\protect\hyperlink{ref-NAC}{8}{]} keeps the shapes of geographic units intact, and changes the size of the shape. This method disconnects areas creating empty space on the display losing the continuity of the spatial display of the statistic. The Dorling cartogram {[}\protect\hyperlink{ref-ACTUC}{7}{]} represents each unit as a circle, sized according to the value of the statistic. The neighbour relationships are mostly maintained by how the circles touch. A similar approach was pioneered by Raisz {[}\protect\hyperlink{ref-RSCW}{9}{]}, using rectangles that tile to align borders of neighbours {[}\protect\hyperlink{ref-CDWCS}{10}{]}. There have been thorough reviews of the array of methods, as suitable for cancer atlas displays {[}\protect\hyperlink{ref-review}{11}{]}, {[}\protect\hyperlink{ref-BCM}{5}{]}.

@@

In order to assess the effectiveness of the hexagon tile map, the lineup protocol {[}\protect\hyperlink{ref-GIIV}{3}{]} from visual inference procedures is employed. The procedures for doing a power comparison of competing plot designed, outlined in {[}\protect\hyperlink{ref-GTPCCD}{13}{]}, are followed. The approach mirrors classical statistical inference.

In classical statistical inference hypothesis testing is conducted by comparing the value of a test statistic on a standard reference distribution, computed assuming the null hypothesis is true. If the value is extreme, the null hypothesis is rejected, because the test statistic value is unlikely to have been so extreme if it was true. In the lineup protocol, the plot plays the role of the test statistic, and the data plot is embedded in a field of null plots. Defining the plot using a grammar of graphics {[}\protect\hyperlink{ref-ggplot2}{14}{]} makes it a functional mapping of the variables and thus, it can be considered to be a statistic. With the same data, two different plots can be considered to be competing statistics, one possibly a more powerful statistic than the other.

@@

Australia is used for the study, with Statistical Area 2 (SA2) {[}\protect\hyperlink{ref-abs2016}{15}{]} as the geographic units. The results should apply broadly to any other geographic area of interest.

@@

For spatial data, null data is stationary data, where the mean, variance and spatial dependence are constant over the geographic units. Stationary data is specified by a variogram model {[}\protect\hyperlink{ref-POG}{16}{]}. Simulating from a variogram model, where the spatial dependence is specified, generates the stationary spatial data used for the null plots. The parameters for the Gaussian model were sill=1, range=0.3 with the variance generated by a standard normal distribution.

The R package \texttt{gstat} {[}\protect\hyperlink{ref-gstat}{17}{]} was used to simulate 144 null sets, 12 data sets for each plot in a lineup, and 12 sets for 12 lineups.

@@

\hypertarget{web-application-to-collect-responses}{%
\subsection{Web application to collect responses}\label{web-application-to-collect-responses}}

The taipan {[}\protect\hyperlink{ref-taipan}{18}{]} package for R was used to create the survey web application.
This structure was altered to collect responses regarding participants demographics and their survey responses.
The survey app contained three tabs, participants were first shown the demographics and consent page.
This asked participants for their Figure-Eight contributor ID, and their consent to the responses being used for analysis. The demographics collected included participants' preferred pronoun, the highest level of education achieved, their age range and whether they had lived in Australia.

After submitting these responses, the survey application switched to the tab of lineups and associated questions. This allowed participants to easily move through the twelve displays and provide their choice, reason for their choice, and level of certainty.

When participants completed the twelve evaluations the survey application triggered a data analysis script. This created a data set with one row per evaluation. Along with the responses to the three questions, the script added the title of the image, which indicated the type of map display, the type of distribution hidden in the lineup, and the location of the data plot. It also calculated the time taken by participant to view each lineup.

Each participant used the internet to access the survey.
The data transfer from the web application to the data set took place using a secure link to the googlesheet used to store results. The application connected to the googlesheet using the googlesheets {[}\protect\hyperlink{ref-sheets}{19}{]} R package when participants opened the application, and interacted again when participants chosen to submit the survey and indicate their completion. At this time it added the participant's responses to the twelve lineup displays as twelve rows of data in the googlesheet.

@@

Participants were recruited to evaluate lineups from the Figure Eight crowdsourcing platform {[}\protect\hyperlink{ref-figeight}{20}{]}.
The lineup protocol expects that the participants are uninvolved judges with no prior knowledge of the data, to avoid inadvertently affecting results. Potential participants needed to have achieved level 2 or level 3 from prior work. The participants were chosen as they have experience with survey tasks that involve evaluating images XXX Did we really choose participants this way??). All participants were at least 18 years old.

@@

The likelihood of detecting the data plot in the lineup can be modelled using a linear mixed effects model.
The R {[}\protect\hyperlink{ref-RCore}{21}{]} \texttt{glmer()} function in the {[}\protect\hyperlink{ref-lme4}{22}{]} package implements generalised linear mixed effect models. The model used includes the two main effects map type and trend model, which gives the fixed effects model to be:

@@

Computation will be done using R {[}\protect\hyperlink{ref-RCore}{21}{]}, with the \texttt{lme4} package {[}\protect\hyperlink{ref-lme4}{22}{]}.

@@

@@

The authors would like to thank the Australian Cancer Atlas team for discussions regarding alternative spatial visualizations, and Professor Kerrie Mengersen and Dr Earl Duncan for regular meetings filled with suggestions and comments. Mitchell O'Hara-Wild was a co-developer of the taipan {[}\protect\hyperlink{ref-taipan}{18}{]} R package for image tagging, used as the base for the web app constructed to collect participant evaluations of lineups. We are thankful for the NUMBATs (Non-Uniform Monash Business Analytics Team) for participating in the pilot study that helped to assess the experimental design and determine an appropriate sample size for the study.

@@

\begin{itemize}
\tightlist
\item
  Additional analysis of the experimental results
\item
  Survey procedure including training materials for the participants
\item
  24 lineups as images, that were used in the experiment
\item
  12 data sets used to construct the lineups
\end{itemize}

The analysis of the work was completed in R {[}\protect\hyperlink{ref-RCore}{21}{]} with the use of the following packages:

\begin{itemize}
\tightlist
\item
  For document creation: rmarkdown {[}\protect\hyperlink{ref-rmarkdown}{23}{]}, rticles {[}\protect\hyperlink{ref-rticles}{24}{]}, knitr {[}\protect\hyperlink{ref-knitr}{25}{]}.
\item
  For lineup creation and data analysis: tidyverse {[}\protect\hyperlink{ref-tidyverse}{26}{]}, nullabor {[}\protect\hyperlink{ref-nullabor}{27}{]}, ggthemes {[}\protect\hyperlink{ref-ggthemes}{28}{]}, RColorBrewer {[}\protect\hyperlink{ref-RColorBrewer}{29}{]}.
\item
  For image displays: cowplot {[}\protect\hyperlink{ref-cowplot}{30}{]}, png {[}\protect\hyperlink{ref-png}{31}{]}, grid {[}\protect\hyperlink{ref-grid}{32}{]}.
\item
  For modelling and presentation of models: gstat {[}\protect\hyperlink{ref-gstat}{17}{]}, lme4 {[}\protect\hyperlink{ref-lme4}{22}{]}, kableExtra {[}\protect\hyperlink{ref-kableExtra}{33}{]}.
\end{itemize}

@@

@@

\leavevmode\hypertarget{ref-review}{}%
11. (2019) Cancer applications of choropleth maps, and the potential of cartograms and alternative map displays. Manuscript submitted for publication.

\leavevmode\hypertarget{ref-BCHLLSW09}{}%
12. Buja A, Cook D, Hofmann H, Lawrence M, Lee E-K, Swayne DF, Wickham H (2009) Statistical inference for exploratory data analysis and model diagnostics. Philosophical Transactions of the Royal Society, A (Invited) 367:4361--4383

\leavevmode\hypertarget{ref-GTPCCD}{}%
13. Hofmann H, Follett L, Majumder M, Cook D (2012) Graphical tests for power comparison of competing designs. IEEE Transactions on Visualization and Computer Graphics 18:2441--2448

\leavevmode\hypertarget{ref-ggplot2}{}%
14. Wickham H (2009) Ggplot2: Elegant graphics for data analysis. Springer New York

\leavevmode\hypertarget{ref-abs2016}{}%
15. (2018) Australian Statistical Geography Standard (ASGS). Australian Bureau of Statistics

\leavevmode\hypertarget{ref-POG}{}%
16. Matheron G (1963) Principles of geostatistics. Economic Geology 58:1246--1266

\leavevmode\hypertarget{ref-gstat}{}%
17. Gräler B, Pebesma E, Heuvelink G (2016) Spatio-temporal interpolation using gstat. The R Journal 8:204--218

\leavevmode\hypertarget{ref-taipan}{}%
18. Kobakian S, O'Hara-Wild M (2018) Taipan: Tool for annotating images in preparation for analysis.

\leavevmode\hypertarget{ref-sheets}{}%
19. Bryan J, Zhao J (2018) Googlesheets: Manage google spreadsheets from r.

\leavevmode\hypertarget{ref-figeight}{}%
20. (2019) The essential high-quality data annotation platform. Figure Eight

\leavevmode\hypertarget{ref-RCore}{}%
21. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria

\leavevmode\hypertarget{ref-lme4}{}%
22. Bates D, Mächler M, Bolker B, Walker S (2015) Fitting linear mixed-effects models using lme4. Journal of Statistical Software 67:1--48

\leavevmode\hypertarget{ref-rmarkdown}{}%
23. Xie Y, Allaire JJ, Grolemund G (2018) R markdown: The definitive guide. Chapman; Hall/CRC, Boca Raton, Florida

\leavevmode\hypertarget{ref-rticles}{}%
24. Allaire J, Xie Y, R Foundation, et al (2019) Rticles: Article formats for r markdown.

\leavevmode\hypertarget{ref-knitr}{}%
25. Xie Y (2014) Knitr: A comprehensive tool for reproducible research in R. Implementing reproducible computational research

\leavevmode\hypertarget{ref-tidyverse}{}%
26. Wickham H, Averick M, Bryan J, et al (2019) Welcome to the tidyverse. Journal of Open Source Software 4:1686

\leavevmode\hypertarget{ref-nullabor}{}%
27. Wickham H, Chowdhury NR, Cook D, Hofmann H (2018) Nullabor: Tools for graphical inference.

\leavevmode\hypertarget{ref-ggthemes}{}%
28. Arnold JB (2019) Ggthemes: Extra themes, scales and geoms for 'ggplot2'.

\leavevmode\hypertarget{ref-RColorBrewer}{}%
29. Neuwirth E (2014) RColorBrewer: ColorBrewer palettes.

\leavevmode\hypertarget{ref-cowplot}{}%
30. Wilke CO (2019) Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'.

\leavevmode\hypertarget{ref-png}{}%
31. Urbanek S (2013) Png: Read and write png images.

\leavevmode\hypertarget{ref-grid}{}%
32. R Core Team (2019) R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria

\leavevmode\hypertarget{ref-kableExtra}{}%
33. Zhu H (2019) KableExtra: Construct complex table with 'kable' and pipe syntax.
